manuscript

### 2023-12-01 scripts/manuscript.qmd
A big strength I identified

>>>>

I appreciate the way you selected using brackets, which made the code cleaner than listing out all options.

One big strength I'd like to learn from your group is that you keep notes (in comments) of what each code chunk is doing. This is a good coding habit I have heard before but haven't incorporated into my own practice. It'll make revisiting old projects so much easier!
